---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grader

<!-- badges: start -->
<!-- badges: end -->

`grader` provides helpful tools for grading, including functions to

- drop assignments, even fractional assignments
- curve scores
- and more

## Installation

You can install the development version of grader from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("duckmayr/grader")
```

## Example

Suppose you had the following set of grades:

```{r example-grades}
set.seed(138)
grades = round(runif(n = 100, min = 0, max = 100))
knitr::kable(data.frame(
    "Low Score" = min(grades),
    "First Quartile" = quantile(grades, probs = 0.25),
    "Mean" = mean(grades), "Median" = median(grades),
    "Third Quartile" = quantile(grades, probs = 0.75),
    "High Score" = max(grades),
    check.names = FALSE
), row.names = FALSE)
plot(density(grades, from = 0, to = 100))
```

But you wanted a more reasonable distribution of the grades...
You can use `grader::curve_grades()`.
It provides two types of curve:

1. A linear curve, matching two raw scores to two target scores and linearly
   adjusting the remaining grades; this is the default behavior, with defaults
   matching the mean raw score to 85 and the 95th percentile score to 95.
2. A "normal" curve, matching the empirical CDF of scores to a normal CDF
   with a specified target mean (default: 85) and specified target standard
   deviation (default: 10) truncated to $[0, 100]$.

Here's an illustration of the default curving behavior (note the x-axis!):

```{r example-linear-curve}
library(grader)
curved_grades = round(curve_grades(scores = grades))
knitr::kable(data.frame(
    "Low Score" = min(curved_grades),
    "First Quartile" = quantile(curved_grades, probs = 0.25),
    "Mean" = mean(curved_grades), "Median" = median(curved_grades),
    "Third Quartile" = quantile(curved_grades, probs = 0.75),
    "High Score" = max(curved_grades),
    check.names = FALSE
), row.names = FALSE)
plot(density(curved_grades, from = 0, to = 100), xlim = c(50, 100))
```

Or the normal curve behavior:

```{r example-normal-curve}
library(grader)
curved_grades = round(curve_grades(scores = grades, method = "normal"))
knitr::kable(data.frame(
    "Low Score" = min(curved_grades),
    "First Quartile" = quantile(curved_grades, probs = 0.25),
    "Mean" = mean(curved_grades), "Median" = median(curved_grades),
    "Third Quartile" = quantile(curved_grades, probs = 0.75),
    "High Score" = max(curved_grades),
    check.names = FALSE
), row.names = FALSE)
plot(density(curved_grades, from = 0, to = 100), xlim = c(50, 100))
```

You can also generate an average of scores after dropping a particular number
of assignments; suppose a student had assignment scores $(0, 95, 0)$; we can
see what the student's average after dropping no assignments, one, two, or
even one and a half assignments (in the case of fractional dropped assignments,
a weighted average is used where the marginal score receives the fractional
weight):

```{r assignment-dropping}
grades = c(0, 95, 0)
knitr::kable(data.frame(
    Dropped = c(0, 1, 1.5, 2),
    Average = sapply(c(0, 1, 1.5, 2), function(x) avg_w_drops(grades, x))
))
```
